Comparing vector-based and ACT-R memory models of tag retrieval:\protect\\User-customized hashtag/tag prediction on Twitter and StackOverflow

### 2014-07-18 writeups/dissertation/dissertation.tex
foo

>>>>

Adding a user's prior tag history as an additional component has been shown to improve performance, but is this always the case?
If enough context information has been collected, maybe a context-only model can perform just as well as a combined context and prior model.
If this were the case, then it may be less important that the random-permutation model does not include a prior term by default.

Full models were tested against context-only models for both sites and both the Bayesian and random-permutation model types.
The four Twitter popular-hashtags datasets and the StackOverflow randomly-sampled datasets were tested first.

The results are included in Figures \ref{figContextPriorneededSO} and \ref{figContextPriorneededT}.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-priorAddSO-crop.pdf}}}
  \caption{Model accuracy for various word order methods for the random-permutation model for Twitter}
  \label{figContextPriorneededSO}
\end{figure}

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-priorAddT-crop.pdf}}}
  \caption{Model accuracy for various word order methods for the random-permutation model for Twitter}
  \label{figContextPriorneededT}
\end{figure}

For both the Bayesian and random-permutation models, accuracy remains the same when the prior compoennt is ermoved for StackOverflow.
Accuracy does dramatically decrease for Twitter when the prior is removed, however.

These results show that prior informatino is not always needed when a large amount of context is avaialble and not much information has been collected about each user's past history.
The StackOverflow randomly-sampled dataset selects posts across the entire dataset, regardless of each user's popularity or tag history.
Across the dataset, each user only asks FIXME questions on average, so there is not a large amount of past tag history available for the prior component to use,
which is why this component is not a strong predictor in this case.

However, can a context-only model perform just as well as a combined context and prior model when users with the largest amount of StackOverflow history are tested?
If each user's tagging history is a useful predictor for StackOverflow,
then this component should at least generate unique predictive variance in the case where users with large amounts of history are tested.

The same StackOverflow popular-users datasets used to test the prior component in isolation were used to test the prior component when context was added.
However, since computing activations for the context component take an order of magnitude more wall-clock time than computing the prior comonent, not all observations could be included for the test.
To reduce the observations, the last FIXME posts from each user in the datasets were sampled.
Using the last observations for each user ensures that the observations tested have aquired the greatest amount of past tagging history in the datasets.
So if a context-only model performs just as well as the full model in this case, it would be surprising.

The results comparing the full model to a context-only only model for the StackOverflow popular-users dataset are included in Figure \ref{figPUAddPrior}.

\begin{figure}[!htbp]
  \scalebox{.8}{\resizebox{\linewidth}{!}{\includegraphics{compareMeanDV-acc-priorAddPUserSO-crop.pdf}}}
  \caption{Unique variance in prior component for popular StackOverflow users}
  \label{figPUAddPrior}
\end{figure}

In this case, past tag history does contain unique variance for accurately predicting tag use.
Accuracy improves for both the Bayesian and random-permutation models when the prior model component is combined with context compared to context alone.

This shows that incorporating past tagging history is important for even a site like StackOverflow where a large amount of context information has been collected.
However, for this type of site it only becomes important when a reasonably large amount of a user's past tagging history has been collected.
For a randomly-sampled user on StackOverflow, a context-only model captures the majority of the predicitve variance.
